Intentional release of native species undermines ecological stability

### 2022-10-21 rmd/manuscript.Rmd
Update manuscript.Rmd

When carrying capacity was small ($K=$ `r min(list_param[[2]]$k)`), our model predicted a destabilizing effect of intentional release on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure** \@ref(fig:figure-layout)**A**). This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure** \@ref(fig:figure-layout)**A**). The enhanced species decreased because release induced the negative competitive effect exceeding the reproductive contribution of released individuals, as reported in a previous theoretical study [@satakeStockingCaptivebredFish2012]. Meanwhile, interspecific competition reduced the unenhanced species, resulting in fewer persisting species (**Figure** \@ref(fig:figure-layout)**A**). Combined, the total community density decreased more sharply than individual species groups (**Figure** \@ref(fig:figure-layout)**A**). The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure** \@ref(fig:figure-layout)**A**). Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV. These patterns were qualitatively similar across ecological contexts with the low carrying capacity (robust to the changes in $r_1$, $\bar{\alpha}$, and $f_R$; **Figures S3 -- S6**).

@@

As predicted, stream fish communities showed greater temporal fluctuations (higher CV) at sites with the intensive release (**Figure** \@ref(fig:figure-layout)**B**). The effect was striking in its magnitude, almost doubling the CV at the highest release level. Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure** \@ref(fig:figure-coef); see **Methods** for the Bayesian estimation of effective release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob), 2)` (**Table S6**). This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)**;** see **Tables S6 -- S8** for full statistics). In the meantime, the SDs had vague relationships with the intentional release (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)).

@@

It is noteworthy that the scale of the release program at the protected watersheds (annual average maximum = `r op(max(df_stock_mu$mean_stock), 2)` million fish) is fairly small when compared with those for other fishery resources [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]. For example, 649.1 million fish are released annually to supplement the pink salmon stock at the Prince William Sound in Alaska, where wild populations seem to be severely compromised due to competition with hatchery fish [@amorosoMeasuringNetBiological2017]. Similarly, the large-scale release of Black sea bream has been conducted in Kagoshima Bay (Japan) since 1974 (the yearly-average of 0.64 million juveniles) with associated declines of wild stocks and genetic diversity [@kitadaRigorousMonitoringLargescale2019]. Although we do not know the carrying capacities of the recipient systems, it is clear that our results should not be viewed as an exceptional case. In support of this view, a meta-analysis revealed that only a few massive release programs in fisheries led to an increased abundance of the focal species [@arakiHatcheryStockingHelp2010]. Yet, none of those studies statistically quantified the community-level impact. Future studies addressing this knowledge gap are therefore desired to generalize our findings.

Human activities are strictly regulated in the protected watersheds, and the near-intact environment (**Figure S10**) may have helped uncover the qualitative agreement between theory and empirical patterns. For example, any form of exploitation, including angling, is prohibited in these areas. In addition, exclusive permission from a governer of Hokkaido is required to physically alter in-stream and riparian habitats. Therefore, unmeasured human influences should have minimal influences on the observed relationships. Further, we have statistically controlled natural variation in environmental factors (see **Methods**). Nevertheless, our results must be viewed with caution: we cannot exclude the possibility of spurious correlations due to the inherent nature of correlative analysis and field research. Since an experimental approach is nearly impossible at this spatial scale, the application of novel causal inferences (e.g., convergent cross mapping) [@sugiharaDetectingCausalityComplex2012; @ushioFluctuatingInteractionNetwork2018; @suzukiDecomposingPredictabilityIdentify2022] may be a potential alternative to confirm the causal relationship between intentional release and community dynamics. Unfortunately, these methods were not applicable to our data because they require a longer and non-sparse time series to yield robust results.

>>>>

When carrying capacity was small ($K=$ `r min(list_param[[2]]$k)`), our model predicted a destabilizing effect of intentional release on ecological communities as illustrated by increased CV with increasing numbers of releases (**Figure** \@ref(fig:figure-layout)**A**). This pattern stemmed mainly from the reduced mean of the total community density, and both enhanced and unenhanced species groups were responsible (**Figure** \@ref(fig:figure-layout)**A**). The enhanced species decreased because release induced the negative competitive effect exceeding the reproductive contribution of released individuals, as reported in a previous theoretical study [@satakeStockingCaptivebredFish2012]. Meanwhile, interspecific competition reduced the unenhanced species, resulting in fewer persisting species (**Figure** \@ref(fig:figure-layout)**A**). Combined, the total community density decreased more sharply than individual species groups (**Figure** \@ref(fig:figure-layout)**A**). The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure** \@ref(fig:figure-layout)**A**). Since a CV is a ratio of an SD to a mean, the steeper decline of the mean community density led to the increased CV. These patterns were qualitatively similar across ecological contexts with the low carrying capacity (**Figures S3 -- S6**), but except for the scenario in which the enhanced species exhibits chaos ($r_1=$ `r max(list_param[[2]]$r1)`).

@@

As predicted, stream fish communities showed greater temporal fluctuations (higher CV) at sites with the intensive release (**Figure** \@ref(fig:figure-layout)**B**). The effect was striking in its magnitude, almost doubling the CV at the highest release level. Our analysis strongly supported the positive relationship between the CV and the number of "effective" releases (**Figure** \@ref(fig:figure-coef); see **Methods** for the Bayesian estimation of effective release), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob) %>% round(2), 2)` (**Table S6**). This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)**;** see **Tables S6 -- S8** for full statistics). In the meantime, the SDs had vague relationships with the intentional release (**Figures** \@ref(fig:figure-layout)**B and** \@ref(fig:figure-coef)).

@@

It is noteworthy that the scale of the release program at the protected watersheds (annual average maximum = `r op(max(df_stock_mu$mean_stock), 2)` million fish) is comparable or even smaller when compared with those for other fishery resources [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]. For example, 649.1 million fish are released annually to supplement the pink salmon stock at the Prince William Sound in Alaska, where wild populations seem to be severely compromised due to competition with hatchery fish [@amorosoMeasuringNetBiological2017]. Similarly, the large-scale release of Black sea bream has been conducted in Kagoshima Bay (Japan) since 1974 (the yearly-average of 0.64 million juveniles) with associated declines of wild stocks and genetic diversity [@kitadaRigorousMonitoringLargescale2019]. Although we do not know the carrying capacities of the recipient systems, it is clear that our results should not be viewed as an exceptional case. In support of this view, a meta-analysis revealed that only a few massive release programs in fisheries led to an increased abundance of the focal species [@arakiHatcheryStockingHelp2010]. Yet, none of those studies statistically quantified the community-level impact. Future studies addressing this knowledge gap are therefore desired to generalize our findings.

Human activities are strictly regulated in the protected watersheds, and the near-intact environment (**Figure S10**) may have helped uncover the qualitative agreement between theory and empirical patterns. For example, any form of exploitation, including angling, is prohibited in these areas. In addition, exclusive permission from the governer of Hokkaido is required to physically alter in-stream and riparian habitats. Therefore, unmeasured human influences should have minimal influences on the observed relationships. Further, we have statistically controlled natural variation in environmental factors (see **Methods**). Nevertheless, our results must be viewed with caution: we cannot exclude the possibility of spurious correlations due to the inherent nature of correlative analysis and field research. Since an experimental approach is nearly impossible at this spatial scale, the application of novel causal inferences (e.g., convergent cross mapping) [@sugiharaDetectingCausalityComplex2012; @ushioFluctuatingInteractionNetwork2018; @suzukiDecomposingPredictabilityIdentify2022] may be a potential alternative to confirm the causal relationship between intentional release and community dynamics. Unfortunately, these methods were not applicable to our data because they require a longer and non-sparse time series to yield robust results.
